Expected Dependency Pair Match: Predicting translation quality with expected syntactic structure

### 2009-08-11 mtjournal.tex
inline citation and notation fix

Alternative measures that 
incorporate synonym knowledge sources include: METEOR
\cite{banerjee05meteor}, which uses synonym tables and
morphological stemming to do progressively more forgiving matching;
%%MO: I am taking out the tuning stuff here since it isn't critical
%It can be tuned towards recall or precision, but is generally not
%tuned by users.  
TER Plus (TERp) \cite{snover09terp}, which is an extension of the
previously-mentioned TER that also incorporates synonym sets and stemming, along
with automatically-derived paraphrase tables.  
%TERp is explicitly
%intended to be tuned to a development set by users.
%
%Tuning has the advantage that the weight of different types of errors
%can be adjusted to match the needs of the task, though it makes it
%more difficult to compare results across tasks, particularly when
%there is little data for tuning.
Other metrics modeling syntactically-local (rather than string-local)
word-sequences include: tree-local
$n$-gram precision in various configurations of constituency and
dependency trees \cite{liu05syntaxformteval};
%%MO: Since sparseval is cited elsewhere, I don't think we need the endnote
%\endnote{The dependency-based SParseval measure
%\cite{roark06:sparseval}, designed as a parse-quality metric for
%speech, is a similar approach, in that it is an F-measure over a
%decomposition of reference and hypothesis trees.} 
and the \textbf{d} and
\textbf{d\_var} measures proposed by \inlinecite{owczarzak07evaluatingmt}
%%MO: This is a hack to get the second year without the name
(2007b) 
that compare relational tuples derived from a
lexical functional grammar (LFG)
over reference and hypothesis translations.\endnote{
  \inlinecite{owczarzak07evaluatingmt} extend their previous line of
  research \cite{owczarzak07labelleddepseval}  by variably-weighting
%%MO: you actually do variable weighting using parse probabilities, so
%% would be good to mention what they use.  If you can say this in a few
%% words, then you won't add a line
  dependencies and by including synonym matching, two directions not
  pursued here. Hence, the earlier paper is cited in comparisons.
}
%
These syntactically-oriented measures require a system for proposing
dependency structure over the reference and hypothesis
translations. \inlinecite{liu05syntaxformteval} use a
PCFG parser with deterministic head-finding, while 
\cite{owczarzak07evaluatingmt} extract the semantic dependency
relations from an LFG parser \cite{cahill04lfg}.
%
This work extends the dependency-scoring strategies of
\inlinecite{owczarzak07evaluatingmt}, which reported substantial
improvement in correlation with human judgment relative to BLEU and
TER, by using a 
publicly-available probabilistic context-free grammar (PCFG) parser and deterministic head-finding rules. In addition, we consider more types of constituents and different score combinations, as well as combination with of synonym-type scores.

MT measures are evaluated in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07evaluatingmt}
comparing the measure to human
judgments of fluency and adequacy.  In other work, e.g.\
\cite{snover06ter}, measures are compared to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we explore both kinds of
evaluation.

We describe our approach to including syntax in MT
evaluation by outlining a family of metrics in
section~\ref{sec:approach} and implementation details in
section~\ref{sec:paradigm}.  Section~\ref{sec:faexpts} examines the
correlation of members of this family with human judgments of
fluency and adequacy, using the 
\cite{owczarzak07evaluatingmt} paradigm to provide comparisons and
select a best case configuration, Expected Dependency Pair Match
(EDPM). The EDPM measure is then compared to BLEU and TER in terms of
correlation with HTER, exploring language/genre effects in
section~\ref{sec:hter1} and combination with TERp's synonym/paraphrase
features in section~\ref{sec:hter2}. Finally, findings and future work
are summarized in section~\ref{sec:conclusion}.

@@

In table~\ref{tab:hterperdoc}, we show per-document Pearson's $r$
between $\overline{\textrm{EDPM}}$ and $\overline{\textrm{HTER}}$, as well as the $\overline{\textrm{TER}}$ and $\overline{\textrm{BLEU}}$$_4$
baselines. EDPM has the highest correlation in each of the
subcorpora created by dividing by genre or by source language, as well
as the corpus as a whole.   In structured data
(\texttt{bn} and \texttt{nw}), these differences are not always
significant, but in the unstructured domains (\texttt{wb} and
\texttt{bc}), EDPM is always significantly better than at least one of
the comparison baselines.

>>>>

Alternative measures that 
incorporate synonym knowledge sources include: METEOR
\cite{banerjee05meteor}, which uses synonym tables and
morphological stemming to do progressively more forgiving matching;
%%MO: I am taking out the tuning stuff here since it isn't critical
%It can be tuned towards recall or precision, but is generally not
%tuned by users.  
TER Plus (TERp) \cite{snover09terp}, which is an extension of the
previously-mentioned TER that also incorporates synonym sets and stemming, along
with automatically-derived paraphrase tables.  
%TERp is explicitly
%intended to be tuned to a development set by users.
%
%Tuning has the advantage that the weight of different types of errors
%can be adjusted to match the needs of the task, though it makes it
%more difficult to compare results across tasks, particularly when
%there is little data for tuning.
Other metrics modeling syntactically-local (rather than string-local)
word-sequences include: tree-local
$n$-gram precision in various configurations of constituency and
dependency trees \cite{liu05syntaxformteval};
%%MO: Since sparseval is cited elsewhere, I don't think we need the endnote
%\endnote{The dependency-based SParseval measure
%\cite{roark06:sparseval}, designed as a parse-quality metric for
%speech, is a similar approach, in that it is an F-measure over a
%decomposition of reference and hypothesis trees.} 
and the \textbf{d} and
\textbf{d\_var} measures proposed by \inlinecite{owczarzak07evaluatingmt}
%%MO: This is a hack to get the second year without the name
(2007b) 
that compare relational tuples derived from a
lexical functional grammar (LFG)
over reference and hypothesis translations.\endnote{
  \inlinecite{owczarzak07evaluatingmt} extend their previous line of
  research \cite{owczarzak07labelleddepseval}  by variably-weighting
%%MO: you actually do variable weighting using parse probabilities, so
%% would be good to mention what they use.  If you can say this in a few
%% words, then you won't add a line
  dependencies and by including synonym matching, two directions not
  pursued here. Hence, the earlier paper is cited in comparisons.
}
%
These syntactically-oriented measures require a system for proposing
dependency structure over the reference and hypothesis
translations. \inlinecite{liu05syntaxformteval} use a
PCFG parser with deterministic head-finding, while 
\inlinecite{owczarzak07evaluatingmt} extract the semantic dependency
relations from an LFG parser \cite{cahill04lfg}.
%
This work extends the dependency-scoring strategies of
\inlinecite{owczarzak07evaluatingmt}, which reported substantial
improvement in correlation with human judgment relative to BLEU and
TER, by using a 
publicly-available probabilistic context-free grammar (PCFG) parser and deterministic head-finding rules. In addition, we consider more types of constituents and different score combinations, as well as combination with of synonym-type scores.

MT measures are evaluated in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07evaluatingmt}
comparing the measure to human
judgments of fluency and adequacy.  In other work, e.g.\
\inlinecite{snover06ter}, measures are compared to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we explore both kinds of
evaluation.

We describe our approach to including syntax in MT
evaluation by outlining a family of metrics in
section~\ref{sec:approach} and implementation details in
section~\ref{sec:paradigm}.  Section~\ref{sec:faexpts} examines the
correlation of members of this family with human judgments of
fluency and adequacy, using the 
\inlinecite{owczarzak07evaluatingmt} paradigm to provide comparisons and
select a best case configuration, Expected Dependency Pair Match
(EDPM). The EDPM measure is then compared to BLEU and TER in terms of
correlation with HTER, exploring language/genre effects in
section~\ref{sec:hter1} and combination with TERp's synonym/paraphrase
features in section~\ref{sec:hter2}. Finally, findings and future work
are summarized in section~\ref{sec:conclusion}.

@@

In table~\ref{tab:hterperdoc}, we show per-document Pearson's $r$
between $\overline{\textrm{EDPM}}$ and $\overline{\textrm{HTER}}$, as well as the $\overline{\textrm{TER}}$ and $\overline{\textrm{BLEU}_4}$
baselines. EDPM has the highest correlation in each of the
subcorpora created by dividing by genre or by source language, as well
as the corpus as a whole.   In structured data
(\texttt{bn} and \texttt{nw}), these differences are not always
significant, but in the unstructured domains (\texttt{wb} and
\texttt{bc}), EDPM is always significantly better than at least one of
the comparison baselines.
